---
output: stevetemplates::cv
geometry: margin=1in

title: "CV"
author: Ulrik Kristoffer Stoltze

jobtitle: "Medical Docter, PhD-student, Course Director, Father, Husband"
address: "C.T. Barfoedsvej 3, 4.th., 2000 Frederiksberg, Denmark"
fontawesome: yes
email: ulrik.kristoffer.stoltze@regionh.dk  
# github: svmiller
twitter: StoltzeUlrik
#osf: "Enter 5 digit osf string here"
phone: "+45 50455575"
# web: guinness.com
updated: TRUE
rdateformat: "`r format(Sys.time(), '%d %b %Y')`"

keywords: R Markdown, academic CV, template

fontfamily: mathpazo
fontfamilyoptions: sc, osf
fontsize: 11pt
linkcolor: blue
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)

options(scipen = 999)

library(tidyverse)
library(scholar)
library(splitstackshape)
library(googlesheets4)
```

```{r}
# Getting bibliometrics from Google Scholar using the scholar R package
# Requires the user ID, which is found in the url for the Google scholar profile page
scholar_ID <- "ZqNYy1MAAAAJ"
google_scholar_url <- paste0("https://scholar.google.com/citations?user=", scholar_ID)
# Extract metrics to build CV text later
n_cites <- get_citation_history(scholar_ID) %>% pull(cites) %>% sum
n_pubs <- get_num_articles(scholar_ID)
n_first_pubs <- author_position(get_publications(scholar_ID)$author, get_profile(scholar_ID)$name) %>% filter(Position == 1) %>% nrow()
# I co-first authored some publications. Google scholar does not take this into account, so this has to be added manually.
n_first_pubs_corrected <- 
  n_first_pubs + 
  1 + # Acta neuropathol., 2022
  1 # Childhood Acute Lymphoblastic Leukemia, 2017

# As an active scientist, you'll have a number of works that are somewhere in the publication pipeline. To reflect this I created a list where I track the process. Accessed with the googlesheets package.
gs4_deauth()
pub_pipeline <- read_sheet("1Nx6ft4gO6JRrAqRjkZ0qPnWtFXv_aKXN6YuBAN4EqIg", range = "pipe")
n_accepted_pubs <- pub_pipeline %>% filter(Status == "Accepted") %>% nrow()
n_revision_review_pubs <- pub_pipeline %>% filter(Status %in% c("Review","Revision")) %>% nrow()
n_submitted_pubs <- pub_pipeline %>% filter(Status == "Submitted") %>% nrow()
n_presubmission_pubs <- pub_pipeline %>% filter(Status %in% c("Analysis","Preparation")) %>% nrow()
n_pipeline_pubs <- n_accepted_pubs+n_revision_review_pubs+n_submitted_pubs+n_presubmission_pubs
papers_paper <- ifelse(n_pipeline_pubs==1,"paper", "papers")

n_old_jobs <- read_sheet("1Nx6ft4gO6JRrAqRjkZ0qPnWtFXv_aKXN6YuBAN4EqIg", range = "old_jobs") %>% nrow()
h_taught <- read_sheet("1Nx6ft4gO6JRrAqRjkZ0qPnWtFXv_aKXN6YuBAN4EqIg", range = "teaching") %>% pull(Duration) %>% sum/60
n_teaching_positions <- read_sheet("1Nx6ft4gO6JRrAqRjkZ0qPnWtFXv_aKXN6YuBAN4EqIg", range = "teaching") %>% distinct(Subject) %>% nrow()
n_conf_speaks <- read_sheet("1Nx6ft4gO6JRrAqRjkZ0qPnWtFXv_aKXN6YuBAN4EqIg", range = "Conferences_and_invited_speaker") %>% nrow()
n_media_appearances <- read_sheet("1Nx6ft4gO6JRrAqRjkZ0qPnWtFXv_aKXN6YuBAN4EqIg", range = "media") %>% nrow()
n_courses <- read_sheet("1Nx6ft4gO6JRrAqRjkZ0qPnWtFXv_aKXN6YuBAN4EqIg", range = "courses_workshops") %>% nrow()
n_visits <- read_sheet("1Nx6ft4gO6JRrAqRjkZ0qPnWtFXv_aKXN6YuBAN4EqIg", range = "clinical_research_stays_abroad") %>% nrow()
```


# Employment

**PhD-student** - _Rigshospitalet, Copenhagen. Supervisor: Kjeld Schmiegelow_ \hfill 2019-*ongoing*  
**Medical Doctor** - _Childhood Cancer Screening Clinic, Rigshospitalet, Copenhagen_ \hfill 2021-*ongoing*  
**Course Director** - _Clinical Genomics at DIS US college, Copenhagen_ \hfill 2016-*ongoing*  
Resident/Introstilling - _Clinical Genetics, Rigshospitalet, Copenhagen_ \hfill 2018-2019  
Intern/KBU - _GI Surgery & General Practice, Herlev Hospital & Copenhagen_ \hfill 2017-2018  
Research Scholar - _Rigshospitalet, Copenhagen. Supervisor: Kjeld Schmiegelow_ \hfill 2015-2016  
Part-time employment - _`r n_old_jobs` student jobs ([full list](https://docs.google.com/spreadsheets/d/1Nx6ft4gO6JRrAqRjkZ0qPnWtFXv_aKXN6YuBAN4EqIg/edit#gid=1077861467))_  \hfill 2002-2017  

# Education
**PhD-student** - _University of Copenhagen_ \hfill 2019-*ongoing*  
Medical Degree/cand.med. - _University of Copenhagen_ \hfill 2017

# Brief bio

> As a physician scientist I have led efforts to DNA sequence every Danish child with cancer since 2016. Our study has complied >1,100 whole genome seqeunces to date. I also spearhead the new Childhood Cancer Screening Clinic, est. 2021, and I am deeply passionate about genomics and disease etiology, and their ability to inform the clinical decisions I make as a doctor.


**Publications:** **`r n_pubs`** works (**`r n_first_pubs_corrected`** as first-author) with a total of **`r n_cites`** citations ([Google Scholar](`r google_scholar_url`) - `r format(Sys.time(), '%d %b %Y')`). Additionally, a total of **`r n_pipeline_pubs`** `r papers_paper` are either accepted (**`r n_accepted_pubs`**), in revision/review (**`r n_revision_review_pubs`**), submitted (**`r n_submitted_pubs`**) or in preparation (**`r n_presubmission_pubs`**).

**Awards/activities:** Young investigator awards (n = **3**, personal/for first-author work; [details](https://docs.google.com/spreadsheets/d/1Nx6ft4gO6JRrAqRjkZ0qPnWtFXv_aKXN6YuBAN4EqIg/edit#gid=81416031)).
**`r n_conf_speaks`** conferences/invited speaker presentations ([details](https://docs.google.com/spreadsheets/d/1Nx6ft4gO6JRrAqRjkZ0qPnWtFXv_aKXN6YuBAN4EqIg/edit#gid=865149923)).
Participated in **`r n_courses`** courses and workshops ([details](https://docs.google.com/spreadsheets/d/1Nx6ft4gO6JRrAqRjkZ0qPnWtFXv_aKXN6YuBAN4EqIg/edit#gid=1863292302)). 
**`r n_media_appearances`** media appearances ([details](https://docs.google.com/spreadsheets/d/1Nx6ft4gO6JRrAqRjkZ0qPnWtFXv_aKXN6YuBAN4EqIg/edit#gid=189459738)). **`r n_visits`** stays with international hospitals as student, doctor or researcher ([details](https://docs.google.com/spreadsheets/d/1Nx6ft4gO6JRrAqRjkZ0qPnWtFXv_aKXN6YuBAN4EqIg/edit#gid=404877154)).
Founder and host of *[Stetoskopet](https://stetoskopet.nu/)*, a medical podcast with 125+ episodes.

**Coding & other skills:** I am highly skilled in `R programming` incl. the use of `Rmarkdown` and `tidyverse`. Also scripted in `unix`, `bash` and `python` on the HPC systems Computerome and NGC cloud. I write and speak English natively. Skilled medical illustator and animator.

**Teaching:** Creator and Director for *Genomics in Clinical Practice* at DIS (US american college level). In total, **`r h_taught`** contact hours of teaching across **`r n_teaching_positions`** teaching positions.

  

\hfill *this document was knitted using a bespoke Rmarkdown script availble on GitHub.*